Stack Safety as a Security Property

### 2020-06-05 main.tex
Words and an example of the ROP thing.

@@

@@

    \paragraph{Observable Integrity}

      Observable integrity is concerned with the changes a callee makes to high integrity components,
      and the effects those writes have on the observable behavior of its caller
      {\it after its return}. Given a contour, a call state, and a returned state, we define
      a ``rollback'' function \(\mathit{roll}_I : \CONTOURS \times \MACHS \times \MACHS
      \rightarrow \MACHS\). The rollback creates a state that matches the call
      state on those components that are high integrity in its contour, and matches the return state
      on low integrity components:

      \[\mathit{roll}_I(\contour,\mach_c,\mach_r)(\component) =
      \begin{cases}
        \mach_c(\component) & \contour(\component) = (\HIGHINT,\_) \\
        \mach_r(\component) & \contour(\component) = (\LOWINT,\_) \\
      \end{cases}\]

      Intuitively, the result of a rollback is an idealized state that reflects changes to accessible
      components, but ignores the callee's interference with the caller's data. Then the observable
      behavior of the resulting trace is the standard to which we expect any real trace to conform.

      A system enjoys observable integrity with regard to \(\callmap\) as follows:

      For any initial state \(\mach_0\), call state \(\mach_c\), and policy state \(\pol_c\) such that
      \(\mpstate{\mach_0}{\mathit{pinit}(\mach_0)} \hookrightarrow ... \mpostate{\mach_c}{\pol_c}{\_} ...\)
      and \(\callmap(\mach_c) = n\), if \(\mpstate{\mach_c}{\pol_c} \hookrightarrow ...
        \mpostate{\mach_r}{\pol_r}{\_} | \ret{\mach_c}\):

          \begin{itemize}
            \item Let \(\contour = \mathit{Cof}(\mach_c,n)\)
            \item Let \(\mach_r' = \mathit{roll}_I(\contour,\mach_c,\mach_r)\), \(\mpstate{\mach_r}{\pol_r}
              \hookrightarrow \MPT\), and \(\mach_r' \hookrightarrow \machT'\)
            \item \(\MPT \sim_P \machT'\)
          \end{itemize}

    \paragraph{Observable Confidentiality}

      Observable confidentiality is concerned with whether high confidentiality data influences
      observable both behavior during and after a call. We define variants given the generalized notion
      of contours:
      \[\mach \approx_\contour \mach' \triangleq \forall \component .
      \contour(\component) = \LOWSEC \rightarrow \mach(\component) = \mach'(\component)\]
      \leo{Move earlier}

      Data that is high confidentiality within a callee due either to being in its caller's frame
      will become low confidentiality if the callee returns.\leo{??} We face a subtle distinction: 
      a callee treats the contents of its caller's frame as secrets, and they should not influence
      its behavior. Nor should the callee be able to influence behavior after its return based
      on the caller's secrets, for instance by copying them to registers that will later be output.
      But the caller itself may still adjust its behavior based on its own secrets. So our property
      relies on another rollback function to preserve changes made by the caller but remove other
      differences between variant states.

      In this case, a confidentiality rollback takes a contour and four states: two call states
      that will be variants, and two return states. It is not symmetric, regarding \(\mach_c\) and \(\mach_r\)
      as the ``real'' call and return, \(\mach_c'\) as a variant and \(\mach_r'\) as a return that follows it.
      \[\begin{split}
        & \mathit{roll}_C(\contour,\mach_c,\mach_c',\mach_r,\mach_r')(\component) = \\
        & \begin{cases}
          \mach_c(\component) & \text{if } C(\component) = \HIGHSEC \text{ and } \\
                  & \mach_c(\component) = \mach_r(\component) \text{ and }
                    \mach_c'(\component) = \mach_r'(\component) \\
          \mach_r'(\component) & \text{else} \\
        \end{cases}
      \end{split}\]
      \leo{Maybe this should be called unscramble}

      A system enjoys observable confidentiality with respect to \(\callmap\) as follows:

      For any initial state \(\mach_0\), call state \(\mach_c\), and policy state \(\pol_c\) such that
      \(\mpstate{\mach_0}{\mathit{pinit}(\mach_0)} \hookrightarrow ... \mpostate{\mach_c}{\pol_c}{\_} ...\) and
      \(\callmap(\mach_c) = n\):

      \begin{itemize}
        \item Let \(\contour = \mathit{Cof}(\mach_c,n)\)
        \item For all \(\mach_c'\) such that \(\mach_c \approx_C \mach_c'\):
        \item If \(\mpstate{\mach_c}{p_c} \hookrightarrow \MPT_1 \mpostate{\mach_r}{\pol_r}{\_} | \ret{\mach_c}\)
          \begin{itemize}
            \item Then there is some \(\mach_r'\) where

              \(\mach_c' \hookrightarrow \machT_1' (\mach_r',\_) | \ret{\mach_c'}\)
            \item Let \(\mach_r'' = \mathit{roll}_C(\contour,\mach_c,\mach_r,\mach_c',\mach_r')\),

              \(\mpstate{\mach_r}{p_r} \hookrightarrow \MPT_2\), and \(\mach_r'' \hookrightarrow \machT_2'\)
            \item \(\MPT_1 \cdot \MPT_2 \sim_P \machT_1' \cdot \machT_2'\)
          \end{itemize}
        \item Else, for \(\MPT\) and \(\machT'\) such that \(\mpstate{\mach_c}{\pol_c} \hookrightarrow \MPT\)
          and \(\mach_c' \hookrightarrow \machT'\), \(\MPT \sim_P \machT'\)
      \end{itemize}

      \leo{Need to fix append. Maybe call it join. It should remove the last
        state of left arg}

>>>>

Confidentiality is in the style of non-interference, comparing the behavior of
a program with an arbitrary variant that preserves low confidentiality data but
may have any configuration of high confidentiality data. We define two machine
states as variants given a contour if they agree on low confidentiality data:
  \[\mach \approx_\contour \mach' \triangleq \forall \component .
    \contour(\component) = \LOWSEC \rightarrow \mach(\component) = \mach'(\component)\]

@@

\sna{Trying to get at why ROP is potentially a problem in non-returning calls
     with an example.}
  \paragraph{Non-stack Resources}

    Stack integrity carries an implicit assumption that memory that has
    become inaccessible should remain so until the correct return state, and
    therefore that a call that never returns fulfills the requirements of
    the property. The caller's integrity is not violated until it is able
    to execute again and finds that its state has changed.

    This assumption might be broken in any number of extended models, such as
    the addition of heap memory or global variables. Suppose a function \(f\)
    has some private state associated with it, with a static guarantee that
    only its instructions access that state. A return oriented programming
    attack from a caller could modify the private state using the caller's own
    instructions, and even without returning, if the callee calls \(f\) the
    modifications will be visible.

    A safety property for such an extended model would extend the contour to
    determine when the security labels of different classes of components
    change, and integrity would mean that when a component is low
    confidentiality, it must have the same value as the last time it was low
    integrity. Stack integrity is a special case in which a component only
    moves from high to low integrity on a return.

@@

    \definition{Observable Integrity}

      Observable integrity weakens eager integrity by allowing a returned state
      to differ from its call state at high integrity components, provided the
      observable behavior of the induced trace from the return matches that of
      an idealized state whose high integrity components do match the call
      state.

      Given a contour, a call state, and a returned state, we define a
      ``rollback'' function \(\mathit{roll} : \CONTOURS \times \MACHS \times
      \MACHS \rightarrow \MACHS\). The rollback returns a state that matches
      the call state on those components that are high integrity in its
      contour, and matches the return state on low integrity components:
      \[\mathit{roll}(\contour,\mach_c,\mach_r)(\component) =
      \begin{cases}
        \mach_c(\component) & \contour(\component) = (\HIGHINT,\_) \\
        \mach_r(\component) & \contour(\component) = (\LOWINT,\_) \\
      \end{cases}\]

      Intuitively, the result of a rollback is an idealized state that
      reflects changes to accessible components, but ignores the callee's
      interference with the caller's data. Then the observable behavior of the
      resulting trace is the standard to which we expect the real trace to
      conform.

      A system enjoys observable integrity with regard to \(\callmap\) if
      for any initial state \(\mach_0\) and each call state \(\mpstatename =
      \mpstate{\mach_c}{\pol_c}\) in the trace induced by
      \(\mpstate{\mach_0}{\mathit{pinit}(\mach_0)}\) where \(\callmap(\mach_c)
      = n\), if there is a return state \(\mpstatename \hookrightarrow \MPT
      \mpostate{\mach_r}{\pol_r}{\_} | \ret{\mach_c}\), the following holds.
      Let \(\contour = \mathit{Cof}(\mach_c,n)\) describe the security levels
      of the call and \(\mach_r' = \mathit{roll}(\contour,\mach_c,\mach_r)\).
      The induced traces \(\mpstate{\mach_r}{\pol_r} \hookrightarrow \MPT\)
      and \(\mach_r' \hookrightarrow \machT'\) must be equivalent up to
      possible policy failure: \(\MPT \sim_P \machT'\).

    \definition{Observable Confidentiality}

      Observable confidentiality is concerned with whether high confidentiality
      data influences observable both behavior during and after a call. As with
      eager confidentiality, we will compare the behavior of the trace induced
      by a state to another induced by its variant. But if the original returns,
      before continuing, we must reset the variant to conform with the original
      state.

      The \(\mathit{restore}\) function takes a contour and four states: the
      original call state, a variant call state, and corresponding return
      states, and returns another state. The resulting state restores those
      components that are high confidentiality to match the original call,
      unless they were changed during execution:
      \[\mathit{restore}(\contour,\mach_c,\mach_c',\mach_r,\mach_r')(\component) =
        \begin{cases}
          \mach_c(\component) & \text{if } \contour(\component) = (\HIGHSEC,\_) \text{ and } \\
                  & \mach_c(\component) = \mach_r(\component) \text{ and }
                    \mach_c'(\component) = \mach_r'(\component) \\
          \mach_r'(\component) & \text{else} \\
        \end{cases}\]

      A system enjoys observable confidentiality with respect to \(\callmap\)
      if for any initial mpstate \(\mpstatename =
      \mpstate{\mach_0}{\mathit{pinit}(\mach_0)}\), each call state
      \(\mpostate{\mach_c}{\pol_c}{\_}\) in the induced trace from
      \(\mpstatename\) where \(\callmap(\mach_c) = n\), and each variant
      \(\mach_c'\) where \(\mach_c \approx_\contour \mach_c'\) and
      \(\contour = \mathit{Cof}(\mach_c, n)\), one of two cases holds on the
      induced traces from \(\mach_c\) and \(\mach_c'\).

      If \(\mpstate{\mach_c}{\pol_c} \hookrightarrow_P \MPT_1 | \ret{\mach_c}\)
      with \(\MPT_1\) the trace within the callee ending with the machine state
      \(\mach_r\) and policy state \(\pol_r\), the first state to return to the
      caller, then the trace from the variant until return 
      \(\mach_c' \hookrightarrow \machT_1 | \ret{\mach_c}\) ends with a return
      state \(\mach_r'\). Let \(\mach_r'' = \mathit{restore}(\contour,\mach_c,
      \mach_c',\mach_r,\mach_r')\), and let the induced traces from the
      returned states be \(\mpstate{\mach_r}{\pol_r} \hookrightarrow_P \MPT_2\)
      and \(\mach_r'' \hookrightarrow \machT_2\). With the callee and caller
      traces joined, the traces are observationally equivalent up to policy
      failures: \(\MPT_1 \cdot \MPT_2 \sim_P \machT_1 \cdot \machT_2\).

      The case in which the induced trace does not return is the same as in the
      eager property: the variant trace also does not return, and the induced
      traces are observationally equivalent up to policy failure.
